Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-07-15 paper/paperv3.qmd
adding histogram for sample size of phenology

```{r}
#| label: fig-pheno
#| fig-cap: "Molting gets shorter but breeding doesn't. A: Observed annual time allocation averaged over individuals. B: Raw data for breeding and molting durations (mean ± se) and predictions (mean and 95% CI) from negative binomial weighted by number of seals obersved per year."
#| fig-width: 4
#| fig-height: 9

@@

@@

(annual_plot | breed_duration_plot | molt_duration_plot) + plot_annotation(tag_levels = "A") + plot_layout(ncol = 1, nrow = 3)
```

>>>>

```{r}
#| label: fig-pheno
#| fig-cap: "Molting gets shorter but breeding doesn't. A: Observed annual time allocation averaged over individuals. B: Raw data for breeding and molting durations (mean ± se) and predictions (mean and 95% CI) from negative binomial weighted by number of seals obersved per year."
#| fig-width: 9
#| fig-height: 9

@@

phen_dist <- seal_phenology %>% 
  # group_by(age) %>% 
  count(age) %>% 
  ggplot(aes(x = age, y = n)) + 
  geom_col(fill = "grey50") + 
  labs(x = "Age (Years)", y = "Number of individuals") + 
  theme()

@@

(annual_plot | phen_dist | breed_duration_plot | molt_duration_plot) + plot_annotation(tag_levels = "A") + plot_layout(ncol = 2, nrow = 2)
```
